Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
Fix typos in intro

In this article we focus on a peculiar category of historical printed books: city trade directories of Paris from the XIX\textsuperscript{th} century (1801 - 1854).
They contain hundred-pages long lists of people, along with their activity and their address; a much valuable fine-grained knowledge to study the social dynamics of the city over time.
Despite containing roughly the same information, the diversity in layouts, information organization and digitizing quality is challenging both for OCR and NER.

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extract texts with OCR, identify directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from the Parisian trade directories.
These directories originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), printed in various layouts, use different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches independently and in combination to assess their usability on the corpus.

The contributions of this article are the following. \joseph{FIXME recheck le plan à la fin}
% Contributions
\begin{enumerate*}[(i)]
    \item We review state of the art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}

>>>>

In this article, we focus on a peculiar category of historical printed books: city trade directories of Paris from the XIX\textsuperscript{th} century (1801 - 1854).
They contain hundred-pages long lists of people, along with their activity and their address, and provide valuable fine-grained knowledge to study the social dynamics of the city over time.
Despite containing roughly the same information, the diversity in layouts, information organization and digitizing quality is challenging both for OCR and NER.

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extracts texts with OCR, identifies directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from Parisian trade directories.
These directories originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), printed in various layouts, use different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches to assess their usability on the corpus.

The contributions of this article are the following.
% Contributions
\begin{enumerate*}[(i)]
    \item We review state of the art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}
